---
title: "Two-Parameters"
format: html
execute: 
  echo: false
---

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(primer.data))
suppressPackageStartupMessages(library(tidymodels))
library(broom)
```

$$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n + \epsilon$$

with $\epsilon \sim \mathcal{N}(0, \sigma^2)$.


```{r}
set.seed(10)

x <- nhanes |>
  filter(age >= 18 & age <= 27) |>
  select(height, sex) |>
  drop_na() |>
  slice_sample(n = 50) 
```

People vary in height. Using 2009‑2011 NHANES data we estimate the average height of new recruits to aid in ordering uniforms before training. 

The distribution of adult heights may have changed since 2011 when the data was collected and estimates obtained using this dataset could render our estimation biased. 


We use a sample of 50 heights to build a model that gives us the DGP. The parameter estimates from the model are

```{r}
#| cache: true
set.seed(10)
x <- nhanes |>
  filter(age >= 18 & age <= 27) |>
  select(height, sex) |>
  drop_na() |>
  slice_sample(n = 50) 

fit_height <- linear_reg() |>
  set_engine("lm") |>
  fit(height ~ sex, data = x)
```

```{r}
# linear_reg() |>
#  set_engine("lm") |>
#  fit(height ~ sex, data = x) |>
# tidy(conf.int = TRUE)
```
```{r}
library(knitr)

# Coefficient table
coef_table <- data.frame(
  Term = c("(Intercept)", "sexMale"),
  Estimate = c(162.18, 15.94)
)

kable(
  coef_table,
  caption = "Table: Coefficients from Linear Model Predicting Height by Sex",
  col.names = c("Term", "Estimate"),
  digits = 2,
  align = "lc"
)
```


 We then compare your actual data (in green) with data that has been simulated from the fitted model, i.e., from the data generating mechanism. 

```{r}
suppressPackageStartupMessages(library(easystats)) # only for console


check_predictions(extract_fit_engine(fit_height))
```

In this case, the distribution of heights in our data closely matches the distributions in the data simulated from our model. 

Our prediction equation with estimated coefficients from the fitted model can be written as 
$$\hat{\text{height}} = 162.18 + 15.94 \cdot \text{sexMale}$$


```{r}
#| cache: true

```